\textbf{Preprinting Microbiology}

### 2017-02-18 submission/Schloss_PrePrints_mBio_2017.tex
Render with eps file instead of tiff

\documentclass[11pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1.0in]{geometry}
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\hypersetup{unicode=true,
            pdftitle={Preprinting Microbiology},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

@@

\textbf{\emph{Background.}} Many scientists, including microbiologists,
have begun to use preprints and other online venues such as social
media, blog posts, and videos as methods to garner attention for their
research and to engage the public. A preprint is an interim research
product, such as an unpublished manuscript, made publicly available
before going through an official peer-review process (1--4). Authors can
post their manuscript to a preprint server for others to read, share,
and comment. Preprints were initially adopted among physicists and
biologists in the 1960s as a method of sharing interesting research
amongst colleagues (5). While the biological community's commitment to
preprints waned, the physics community adopted what is now the
\emph{arXiv} (pronounced ``archive'') preprint server that was hosted at
the Los Alamos National Laboratories from 1991 to 1999 and then at
Cornell University (6). For some physicists and mathematicians, posting
a preprint to \emph{arXiv} followed by submission to a peer-reviewed
journal has become a standard publication pathway. Although \emph{arXiv}
has hosted a number of computational biology papers, the server has not
drawn widespread attention from biologists. Among proponents of
\emph{arXiv}, preprints have aided in the development of research
communication by accelerating the release of the science and helping it
to achieve a wider audience for critique and reception (7). Considering
the broadening adoption of preprints among microbiologists, we sought to
explore the specific uses of and concerns regarding preprints.

\textbf{\emph{Landscape of preprint servers.}} In 2013, two preprint
servers, the \emph{bioRxiv} (pronounced ``bio-archive'') and \emph{PeerJ
Preprints}, were launched as preprint servers for biologists that would
parallel \emph{arXiv} (8). Both platforms offer similar features:
preprint posting is free; each preprint receives a digital object
identifier (DOI) that facilitates the ability to cite preprints in other
scholarly work; if the preprint is ever published, the preprint is
linked to the published version; the submission process for both options
is relatively simple allowing authors to upload a PDF version of their
preprint and supplemental materials; preprints are typically publicly
available in about 24 hours; they have built in venues for authors to
discuss their research with people who leave comments on the manuscript;
preprints undergo a basic screening process to remove submissions with
offensive or non-scientific content; and the sites provide article-level
metrics indicating the number of times an abstract has been accessed or
the preprint has been downloaded. There are several important
differences between the two options. First, \emph{PeerJ Prints} is a
for-profit organization and \emph{bioRxiv} is a non-profit organization
sponsored by Cold Spring Harbor Laboratory. This difference can be
meaningful to authors since some journals, including the American
Society for Microbiology (ASM) Journals, will only accept submissions
that have been posted on preprint servers hosted by non-profit
organizations. Second, preprints at \emph{PeerJ Preprints} are posted
under the Creative Commons Attribution License (CC-BY) and
\emph{bioRxiv} preprints can be posted under one of four CC-BY licenses
or with no permission for reuse. This can be relevant for authors hoping
to submit their work to a journal as journals will not consider
manuscripts posted as preprints under a CC-BY license (e.g.
\emph{Proceedings of the National Academy of Sciences}). We particularly
like the \emph{bioRxiv} licensing flexibility, which empowers authors to
choose the model that best suits them, while ensuring the rapid posting
of their research resultsl however, it is important to provide clear
information to authors on the legal and practical tradeoffs of each
option. A cosmetic, but still relevant difference between the two is the
layout and feel of the two websites. Compared to the \emph{bioRxiv}
site, the \emph{PeerJ Preprint} site is more fluid, gives readers the
ability to ``follow'' a preprint, and provides better access to article
keywords and the ability to search preprints. With broader acceptance of
preprints by traditional journals, many journals, including all of the
ASM journals, have established mechanisms to directly submit manuscripts
that are posted as preprints on \emph{bioRxiv}. It is only possible to
transfer a \emph{PeerJ Preprint} for submission to \emph{PeerJ}. In many
ways, preprint servers have taken on the feel of a journal. As adoption
of this approach expands, it is likely that the features of these sites
will continue to improve. It is also likely that interfaces from
third-parties will improve. For example, although Google Scholar
includes preprints hosted at \emph{bioRxiv} and \emph{PeerJ Preprints}
in their search results, PubMed and Web of Science do not. There is also
hope that the National Institutes of Health (NIH) will renew their
interest in indexing preprints as separate research products than
peer-reviewed publications. As preprint servers begin to look and act
like traditional journals by incorporating features and interfaces, we
think that it is important to value the strength of the preprint - that
of an interim research product, nimble and quickly posted. It is
therefore essential to balance the requirements placed on authors for
features associated with preprints with the current desirable efficiency
of the preprint format.

@@

\textbf{\emph{Metrics for microbiology-affiliated preprints.}} To
analyze the use of preprints, we downloaded the \emph{bioRxiv} on
December 31, 2016. We chose to analyze \emph{bioRxiv} preprints because
these preprints are amenable for submission to ASM journals and there
were 7,434 \emph{bioRxiv} preprints compared to the 2,650 available at
\emph{PeerJ Preprint}. Among the 7,434 preprints on bioRxiv, 329 were
assigned by the authors into the Microbiology category. One limitation
of the \emph{bioRxiv} interface is the inability to assign manuscripts
to multiple categories or to tag the content of the preprint. For
example, this manuscript could be assigned to either the Microbiology or
the Scientific Communication and Education categories. To counter this
limitation, we developed a more permissive approach that classified
preprints as being microbiology-affiliated if their title or abstract
had words containing \emph{yeast}, \emph{fung}, \emph{viral},
\emph{virus}, \emph{archaea}, \emph{bacteri}, \emph{microb},
\emph{microorganism}, or \emph{pathogen}. We identified 1,228 additional
manuscripts that we considered microbiology-affiliated. These
microbiology-affiliated preprints were primarily assigned to the
Evolutionary Biology (N=221), Genomics (N=184), or Bioinformatics
(N=182) categories.

@@

As stated above, preprints offer researchers the opportunity to improve
the quality of their work by adding a more formal and public step to the
scientific process. Among the microbiology-affiliated preprints, 146
(9.3\%) had been commented on at least once and only 35 (2.2\%) more
than three times using the \emph{bioRxiv}-hosted commenting feature.
Although the hosted commenting is only one mechanism for peer review,
this result was somewhat disturbing since the preprint model implicitly
depends on people's willingness to offer others feedback. We understand
that it is not in the tradition of the scientific community to comment
publicly online about colleagues' research results. We think this will
change given the possibilities of new media, and possibly incentives for
open commenting and reviewing could shift the trend. Importantly,
authors do appear to be incorporating feedback from colleagues or
editorial insights from journals as 404 (25.8\%) of preprints were
revised at least once. Among the preprints posted prior to January 1,
2016, 31.6\% of the Microbiology category preprints, 35.1\% of the
microbiology-affiliated preprints, and 33.8\% of all preprints have been
published. As noted above, not all authors submit their preprints to
journals. This would indicate that the ``acceptance rates'' are actually
higher. Regardless, considering that these acceptance rates are higher
than many peer-reviewed journals (e.g.~approximately 20\% at ASM
Journals), these results dispel the critique that preprints represent
overly preliminary research.

Measuring the impact and significance of scientific research is
notoriously difficult. Using several metrics we sought to quantify the
effect that broadly defined microbiology-affiliated preprints have had
on the work of others. Using the download statistics associated with
each preprint, we found that the median number of times an abstract or
PDF had been accessed was 923 (IQR: 603 to 1445) and 303 (IQR: 167 to
568), respectively. These values represent two aspects of posting a
preprint. First, they reflect the number of times people were able to
access science before it was published. Second, they reflect the number
of times people were able to access a version of a manuscript that is
published behind a paywall. To obtain a measure of a preprint's ability
to garner attention and engage the public, we obtained the Altmetric
Attention Score for each preprint (\textbf{Figure 1B}). The Altmetric
Attention Score measures the number of times a preprint or paper is
mentioned in social media, traditional media, Wikipedia, policy
documents, and other sources (33). A higher score indicates that a
preprint received more attention. Microbiology-affiliated preprints have
had a median Altmetric Attention Score of 7.3 (IQR: 3.2 to 16.3) and
those of all preprints hosted at \emph{bioRxiv} have had a median score
of 7.0 (IQR: 3 to 15.6). For comparison, the median Altmetric Attention
Score for articles published in \emph{mBio} published since 2013 was 4.5
(IQR: 1.2 to 13.6). Of all scholarship tracked by Altmetric, the median
Altmetric Attention Score for preprints posted at \emph{bioRxiv} ranks
at the 86 percentile (IQR: 66 to 94. A more traditional and
controversial metric of impact has been the number of citations an
article receives. We obtained the number of citations for the published
versions of manuscripts that were initially posted as preprints. To
allow for a comparison to traditional journals, we considered the
citations for preprints published in 2014 and 2015 as aggregated by Web
of Science (\textbf{Figure 1C}). Among the preprints that were published
and could be found in the Web of Science database, the median number of
citations was 6.5 (IQR: 2-14; mean: 13.6). For comparison, for the
papers published in \emph{mBio} in 2014 and 2015, the median number of
citations was 5 (IQR: 2-9; mean: 6.7). Although it is impossible to
quantify the quality or impact of research with individual metrics, it
is clear that preprints and the publications that result from them are
broadly accepted by the microbiology community.

\textbf{\emph{Preprints from an author's perspective.}} Posting research
as a preprint gives an author great control over when their work is made
public. Under the traditional peer-review model, an author may need to
submit and revise their work multiple times to several journals over a
long period before it is finally published. In contrast, an author can
post the preprint at the start of the process for others to consume and
comment on as it works its way through the editorial process. A first
example illustrates the utility of preprints for improving access to
research and the quality of its reporting. In 2014, the Schloss
laboratory posted a preprint to \emph{PeerJ Preprints} describing a
method of sequencing 16S rRNA gene sequences using the Pacific
Biosciences sequencing platform (34). At the same time, they submitted
the manuscript for review at \emph{PeerJ}. While the manuscript was
under review, they received feedback from an academic scientist and from
scientists at Pacific Biosciences that the impact of the results could
be enhanced by using a recently released version of the sequencing
chemistry. Instead of ignoring this feedback and resubmitting the
manuscript to address the reviews, we generated new data and submitted
an updated preprint a year later with a simultaneous submission to
\emph{PeerJ} that incorporated the original reviews as well as the
feedback we received from the academic scientist and Pacific
Biosciences. It was eventually published by \emph{PeerJ} (35, 36). Since
2015, we have continued to post manuscripts as preprints at the same
time as we have submitted manuscripts. Although the feedback to other
manuscripts has not been as helpful as our initial experience, we were
able to sidestep lengthy review processes by immediately making our
results available; in one case our preprint was available 7 months ahead
of the final published version (37, 38). As a second example, this
manuscript was posted to \emph{bioRxiv} as a preprint on
\textbf{February XX, 2017}. We then solicited feedback on the manuscript
using social media. Two weeks later, we incorporated the comments and
posted a revised preprint and submitted the manuscript to \emph{mBio}.
During that time, the abstract was read \textbf{XXXX} times and the PDF
was accessed \textbf{XXXX} times. This process engaged \textbf{XXXX}
commenters on \emph{bioRxiv}, \textbf{XXXX} people on Twitter,
\textbf{XXXX} on Facebook, and \textbf{XXXX} via email. We received
useful feedback from \textbf{XXX} people. Compared to the two or three
scientists that typically review a manuscript, this experience engaged a
much larger and more diverse community than had we foregone the posting
of a preprint. Although there are concerns regarding the quality of the
science posted to a preprint server, we contend that responsible use of
preprints as a part of the scientific process can significantly enhance
the science.

\textbf{\emph{Preprints from a publisher's perspective.}} A lingering
question is what role traditional journals will have in disseminating
research if there is broad adoption of preprints. We think that edited
peer-reviewed journals offer, and will continue to offer significant
added value to a publication. A scholarly publishing ecosystem in which
preprints coexist with journals will allow authors to gain value from
the immediate communication of their work associated with preprints and
also benefit from the peer-reviewed, professionally edited publication
that publishers can provide. The professional copyediting, layout, and
publicity that these publishers offer are also unique features of
traditional journals. An alternative perspective is that preprints will
eventually replace traditional journals. Certainly, this is a radical
perspective, but it does serve to motivate publishers to capture the
innovation opportunities offered by preprints. By adopting
preprint-friendly policies, journals can create an attractive
environment for authors. As discussed above, a growing number of
journals have created mechanisms for authors to directly submit
preprints to their journals. An example is offered by the ASM, which
earlier this year launched a new venture from \emph{mSphere}.
mSphereDirect is a publication track of the journal that capitalizes on
the opportunity offered to couple preprints with rigorous peer-review.
mSphereDirect. actively encourages authors to post their manuscripts as
preprints as part of an author-driven editorial process where an
editorial decision is rendered within five days and publication in
\emph{mSphere} within a month (39). ASM is developing a new platform,
MicroNow, which will help coalesce specific communities within the
microbial sciences, further enhancing the use of preprints as well as
published articles. In addition to integrating preprints into the
traditional editorial process, several professional societies have also
explicitly supported citation of preprints in their other publications
and recognize the priority of preprints in the literature (14--16).
These are policies that empower authors and make specific journals more
attractive. Other practices have great potential to improve the
reputation of journals. As measured above, preprints are able to garner
attention on par with papers published in highly selective microbiology
journals. Thus, it is in a journal's best interest to recruit these
preprints to their journals. Several journals including \emph{PLOS
Genetics} and \emph{Genome Biology} have publicly stated that they scout
preprints for this purpose (40, 41). Preprints can also be viewed as a
lost opportunity to journals. A preprint that garners significant
attention may be ignored when it is finally published, brining little
additional attention to the journal. Going forward, it will be
interesting to see the innovative approaches that publishers develop so
that they can benefit by incorporating preprints into their process and
whether publishers' influence is reduced by the widespread adoption of
preprints.

@@

This work was supported in part by funding to PDS from the National
Institutes of Health (P30DK034933). We appreciate the support of
Altmetric, Inc and Thompson Reuters who provided advanced programming
interface (API) access to their databases. The workflow utilized
commands in GNU make (v.3.81), GNU bash (v.4.1.2), and R (v.3.3.2).
Within R we utilized the cowplot (v.0.6.3), dplyr (v.0.5.0), ggplot2
(v.2.2.0.9000), httr (v.1.2.1), RCurl (v.1.95-4.8), rentrez (v.1.0.4),
rjson (v.0.2.15), rvest (v.0.3.2.9000), sportcolors (v.0.0.1), and tidyr
(v.0.6.0) packages. A reproducible version of this manuscript and
analysis is available at
\url{http://www.github.com/SchlossLab/Schloss_PrePrints_mBio_2017}.

@@

\subsection*{References}\label{references}
\addcontentsline{toc}{subsection}{References}

\hypertarget{refs}{}
\hypertarget{ref-Vale2015}{}
1. \textbf{Vale RD}. 2015. Accelerating scientific publication in
biology. Proceedings of the National Academy of Sciences
\textbf{112}:13439--13446.
doi:\href{https://doi.org/10.1073/pnas.1511912112}{10.1073/pnas.1511912112}.

\hypertarget{ref-DesjardinsProulx2013}{}
2. \textbf{Desjardins-Proulx P}, \textbf{White EP}, \textbf{Adamson JJ},
\textbf{Ram K}, \textbf{Poisot T}, \textbf{Gravel D}. 2013. The case for
open preprints in biology. PLoS Biology \textbf{11}:e1001563.
doi:\href{https://doi.org/10.1371/journal.pbio.1001563}{10.1371/journal.pbio.1001563}.

>>>>

\documentclass[11pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1.0in]{geometry}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Preprinting Microbiology},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

@@

\textbf{\emph{Background.}} Many scientists, including microbiologists,
have begun to use preprints and other online venues such as social
media, blog posts, and videos as methods to garner attention for their
research and to engage the public. A preprint is an interim research
product, such as an unpublished manuscript, made publicly available
before going through an official peer-review process (1--4). Authors can
post their manuscript to a preprint server for others to read, share,
and comment. Preprints were initially adopted among physicists and
biologists in the 1960s as a method of sharing interesting research
amongst colleagues (5). While the biological community's commitment to
preprints waned, the physics community adopted what is now the
\emph{arXiv} (pronounced ``archive'') preprint server that was hosted at
the Los Alamos National Laboratories from 1991 to 1999 and then at
Cornell University (6). For some physicists and mathematicians, posting
a preprint to \emph{arXiv} followed by submission to a peer-reviewed
journal has become a standard publication pathway. Although \emph{arXiv}
has hosted a number of computational biology papers, the server has not
drawn widespread attention from biologists. Among proponents of
\emph{arXiv}, preprints have aided in the development of research
communication by accelerating the release of the science and helping it
to achieve a wider audience for critique and reception (7). Considering
the broadening adoption of preprints among microbiologists, I sought to
explore the specific uses of and concerns regarding preprints.

\textbf{\emph{Landscape of preprint servers.}} In 2013, two preprint
servers, the \emph{bioRxiv} (pronounced ``bio-archive'') and \emph{PeerJ
Preprints}, were launched as preprint servers for biologists that would
parallel \emph{arXiv} (8). Both platforms offer similar features:
preprint posting is free; each preprint receives a digital object
identifier (DOI) that facilitates the ability to cite preprints in other
scholarly work; if the preprint is ever published, the preprint is
linked to the published version; the submission process for both options
is relatively simple allowing authors to upload a PDF version of their
preprint and supplemental materials; preprints are typically publicly
available in about 24 hours; they have built in venues for authors to
discuss their research with people who leave comments on the manuscript;
preprints undergo a basic screening process to remove submissions with
offensive or non-scientific content; and the sites provide article-level
metrics indicating the number of times an abstract has been accessed or
the preprint has been downloaded. There are several important
differences between the two options. First, \emph{PeerJ Prints} is a
for-profit organization and \emph{bioRxiv} is a non-profit organization
sponsored by Cold Spring Harbor Laboratory. This difference can be
meaningful to authors since some journals, including the American
Society for Microbiology (ASM) Journals, will only accept submissions
that have been posted on preprint servers hosted by non-profit
organizations. Second, preprints at \emph{PeerJ Preprints} are posted
under the Creative Commons Attribution License (CC-BY) and
\emph{bioRxiv} preprints can be posted under one of four CC-BY licenses
or with no permission for reuse. This can be relevant for authors hoping
to submit their work to a journal as journals will not consider
manuscripts posted as preprints under a CC-BY license (e.g.
\emph{Proceedings of the National Academy of Sciences}). The flexibility
of the \emph{bioRxiv} licensing empowers authors to choose the model
that best suits them, while ensuring the rapid posting of their research
results however, it is important to provide clear information to authors
on the legal and practical tradeoffs of each option. A cosmetic, but
still relevant difference between the two is the layout and feel of the
two websites. Compared to the \emph{bioRxiv} site, the \emph{PeerJ
Preprint} site is more fluid, gives readers the ability to ``follow'' a
preprint, and provides better access to article keywords and the ability
to search preprints. With broader acceptance of preprints by traditional
journals, many journals, including all of the ASM journals, have
established mechanisms to directly submit manuscripts that are posted as
preprints on \emph{bioRxiv}. It is only possible to transfer a
\emph{PeerJ Preprint} for submission to \emph{PeerJ}. In many ways,
preprint servers have taken on the feel of a journal. As adoption of
this approach expands, it is likely that the features of these sites
will continue to improve. It is also likely that interfaces from
third-parties will improve. For example, although Google Scholar
includes preprints hosted at \emph{bioRxiv} and \emph{PeerJ Preprints}
in their search results, PubMed and Web of Science do not. There is also
hope that the National Institutes of Health (NIH) will renew their
interest in indexing preprints as separate research products than
peer-reviewed publications. As preprint servers begin to look and act
like traditional journals by incorporating features and interfaces, it
is important to value the strength of the preprint - that of an interim
research product, nimble and quickly posted. It is therefore essential
to balance the requirements placed on authors for features associated
with preprints with the current desirable efficiency of the preprint
format.

@@

\textbf{\emph{Metrics for microbiology-affiliated preprints.}} To
analyze the use of preprints, I downloaded the \emph{bioRxiv} on
December 31, 2016. I chose to analyze \emph{bioRxiv} preprints because
these preprints are amenable for submission to ASM journals and there
were 7,434 \emph{bioRxiv} preprints compared to the 2,650 available at
\emph{PeerJ Preprint}. Among the 7,434 preprints on bioRxiv, 329 were
assigned by the authors into the Microbiology category. One limitation
of the \emph{bioRxiv} interface is the inability to assign manuscripts
to multiple categories or to tag the content of the preprint. For
example, this manuscript could be assigned to either the Microbiology or
the Scientific Communication and Education categories. To counter this
limitation, I developed a more permissive approach that classified
preprints as being microbiology-affiliated if their title or abstract
had words containing \emph{yeast}, \emph{fung}, \emph{viral},
\emph{virus}, \emph{archaea}, \emph{bacteri}, \emph{microb},
\emph{microorganism}, or \emph{pathogen}. I identified 1,228 additional
manuscripts that I considered microbiology-affiliated. These
microbiology-affiliated preprints were primarily assigned to the
Evolutionary Biology (N=221), Genomics (N=184), or Bioinformatics
(N=182) categories.

@@

As stated above, preprints offer researchers the opportunity to improve
the quality of their work by adding a more formal and public step to the
scientific process. Among the microbiology-affiliated preprints, 146
(9.3\%) had been commented on at least once and only 35 (2.2\%) more
than three times using the \emph{bioRxiv}-hosted commenting feature.
Although the hosted commenting is only one mechanism for peer review,
this result was somewhat disturbing since the preprint model implicitly
depends on people's willingness to offer others feedback. Although it is
not in the tradition of the scientific community to comment publicly
online about colleagues' research results, I am optimistic that this
will change given the possibilities of new media, and possibly
incentives for open commenting and reviewing could shift the trend.
Importantly, authors do appear to be incorporating feedback from
colleagues or editorial insights from journals as 404 (25.8\%) of
preprints were revised at least once. Among the preprints posted prior
to January 1, 2016, 31.6\% of the Microbiology category preprints,
35.1\% of the microbiology-affiliated preprints, and 33.8\% of all
preprints have been published. As noted above, not all authors submit
their preprints to journals. This would indicate that the ``acceptance
rates'' are actually higher. Regardless, considering that these
acceptance rates are higher than many peer-reviewed journals
(e.g.~approximately 20\% at ASM Journals), these results dispel the
critique that preprints represent overly preliminary research.

Measuring the impact and significance of scientific research is
notoriously difficult. Using several metrics I sought to quantify the
effect that broadly defined microbiology-affiliated preprints have had
on the work of others. Using the download statistics associated with
each preprint, I found that the median number of times an abstract or
PDF had been accessed was 923 (IQR: 603 to 1445) and 303 (IQR: 167 to
568), respectively. These values represent two aspects of posting a
preprint. First, they reflect the number of times people were able to
access science before it was published. Second, they reflect the number
of times people were able to access a version of a manuscript that is
published behind a paywall. To obtain a measure of a preprint's ability
to garner attention and engage the public, I obtained the Altmetric
Attention Score for each preprint (\textbf{Figure 1B}). The Altmetric
Attention Score measures the number of times a preprint or paper is
mentioned in social media, traditional media, Wikipedia, policy
documents, and other sources (33). A higher score indicates that a
preprint received more attention. Microbiology-affiliated preprints have
had a median Altmetric Attention Score of 7.3 (IQR: 3.2 to 16.3) and
those of all preprints hosted at \emph{bioRxiv} have had a median score
of 7.0 (IQR: 3 to 15.6). For comparison, the median Altmetric Attention
Score for articles published in \emph{mBio} published since 2013 was 4.5
(IQR: 1.2 to 13.6). Of all scholarship tracked by Altmetric, the median
Altmetric Attention Score for preprints posted at \emph{bioRxiv} ranks
at the 86 percentile (IQR: 66 to 94. A more traditional and
controversial metric of impact has been the number of citations an
article receives. I obtained the number of citations for the published
versions of manuscripts that were initially posted as preprints. To
allow for a comparison to traditional journals, I considered the
citations for preprints published in 2014 and 2015 as aggregated by Web
of Science (\textbf{Figure 1C}). Among the preprints that were published
and could be found in the Web of Science database, the median number of
citations was 6.5 (IQR: 2-14; mean: 13.6). For comparison, for the
papers published in \emph{mBio} in 2014 and 2015, the median number of
citations was 5 (IQR: 2-9; mean: 6.7). Although it is impossible to
quantify the quality or impact of research with individual metrics, it
is clear that preprints and the publications that result from them are
broadly accepted by the microbiology community.

\textbf{\emph{Preprints from an author's perspective.}} Posting research
as a preprint gives an author great control over when their work is made
public. Under the traditional peer-review model, an author may need to
submit and revise their work multiple times to several journals over a
long period before it is finally published. In contrast, an author can
post the preprint at the start of the process for others to consume and
comment on as it works its way through the editorial process. A first
example illustrates the utility of preprints for improving access to
research and the quality of its reporting. In 2014, my research group
posted a preprint to \emph{PeerJ Preprints} describing a method of
sequencing 16S rRNA gene sequences using the Pacific Biosciences
sequencing platform (34). At the same time, they submitted the
manuscript for review at \emph{PeerJ}. While the manuscript was under
review, they received feedback from an academic scientist and from
scientists at Pacific Biosciences that the impact of the results could
be enhanced by using a recently released version of the sequencing
chemistry. Instead of ignoring this feedback and resubmitting the
manuscript to address the reviews, we generated new data and submitted
an updated preprint a year later with a simultaneous submission to
\emph{PeerJ} that incorporated the original reviews as well as the
feedback we received from the academic scientist and Pacific
Biosciences. It was eventually published by \emph{PeerJ} (35, 36). Since
2015, we have continued to post manuscripts as preprints at the same
time as we have submitted manuscripts. Although the feedback to other
manuscripts has not been as helpful as our initial experience, we were
able to sidestep lengthy review processes by immediately making our
results available; in one case our preprint was available 7 months ahead
of the final published version (37, 38). As a second example, this
manuscript was posted to \emph{bioRxiv} as a preprint on
\textbf{February XX, 2017}. I then solicited feedback on the manuscript
using social media. Two weeks later, I incorporated the comments and
posted a revised preprint and submitted the manuscript to \emph{mBio}.
During that time, the abstract was read \textbf{XXXX} times and the PDF
was accessed \textbf{XXXX} times. This process engaged \textbf{XXXX}
commenters on \emph{bioRxiv}, \textbf{XXXX} people on Twitter,
\textbf{XXXX} on Facebook, and \textbf{XXXX} via email. I received
useful feedback from \textbf{XXX} people. Compared to the two or three
scientists that typically review a manuscript, this experience engaged a
much larger and more diverse community than had I foregone the posting
of a preprint. Although there are concerns regarding the quality of the
science posted to a preprint server, I contend that responsible use of
preprints as a part of the scientific process can significantly enhance
the science.

\textbf{\emph{Preprints from a publisher's perspective.}} A lingering
question is what role traditional journals will have in disseminating
research if there is broad adoption of preprints. Edited peer-reviewed
journals offer and will continue to offer significant added value to a
publication. A scholarly publishing ecosystem in which preprints coexist
with journals will allow authors to gain value from the immediate
communication of their work associated with preprints and also benefit
from the peer-reviewed, professionally edited publication that
publishers can provide. The professional copyediting, layout, and
publicity that these publishers offer are also unique features of
traditional journals. An alternative perspective is that preprints will
eventually replace traditional journals. Certainly, this is a radical
perspective, but it does serve to motivate publishers to capture the
innovation opportunities offered by preprints. By adopting
preprint-friendly policies, journals can create an attractive
environment for authors. As discussed above, a growing number of
journals have created mechanisms for authors to directly submit
preprints to their journals. An example is offered by the ASM, which
earlier this year launched a new venture from \emph{mSphere}.
mSphereDirect is a publication track of the journal that capitalizes on
the opportunity offered to couple preprints with rigorous peer-review.
mSphereDirect. actively encourages authors to post their manuscripts as
preprints as part of an author-driven editorial process where an
editorial decision is rendered within five days and publication in
\emph{mSphere} within a month (39). ASM is developing a new platform,
MicroNow, which will help coalesce specific communities within the
microbial sciences, further enhancing the use of preprints as well as
published articles (Stefano Bertuzzi, personal communication). In
addition to integrating preprints into the traditional editorial
process, several professional societies have also explicitly supported
citation of preprints in their other publications and recognize the
priority of preprints in the literature (14--16). These are policies
that empower authors and make specific journals more attractive. Other
practices have great potential to improve the reputation of journals. As
measured above, preprints are able to garner attention on par with
papers published in highly selective microbiology journals. Thus, it is
in a journal's best interest to recruit these preprints to their
journals. Several journals including \emph{PLOS Genetics} and
\emph{Genome Biology} have publicly stated that they scout preprints for
this purpose (40, 41). Preprints can also be viewed as a lost
opportunity to journals. A preprint that garners significant attention
may be ignored when it is finally published, brining little additional
attention to the journal. Going forward, it will be interesting to see
the innovative approaches that publishers develop so that they can
benefit by incorporating preprints into their process and whether
publishers' influence is reduced by the widespread adoption of
preprints.

@@

I am grateful to Stefano Bertuzzi and Lynn Enquist for their helpful
comments on earlier versions of this manuscript. This work was supported
in part by funding to PDS from the National Institutes of Health
(P30DK034933). I appreciate the support of Altmetric, Inc and Thompson
Reuters who provided advanced programming interface (API) access to
their databases. The workflow utilized commands in GNU make (v.3.81),
GNU bash (v.4.1.2), and R (v.3.3.2). Within R I utilized the cowplot
(v.0.6.9990), dplyr (v.0.5.0), ggplot2 (v.2.1.0.9001), httr (v.1.2.1),
RCurl (v.1.95-4.8), rentrez (v.1.0.4), rjson (v.0.2.15), rvest
(v.0.3.2), sportcolors (v.0.0.1), and tidyr (v.0.6.0) packages. A
reproducible version of this manuscript and analysis is available at
\url{http://www.github.com/SchlossLab/Schloss_PrePrints_mBio_2017}.

@@

\hyperdef{}{references}{\label{references}}
\subsection*{References}\label{references}
\addcontentsline{toc}{subsection}{References}

\hyperdef{}{ref-Vale2015}{\label{ref-Vale2015}}
1. \textbf{Vale RD}. 2015. Accelerating scientific publication in
biology. Proceedings of the National Academy of Sciences
\textbf{112}:13439--13446.
doi:\url{http://doi.org/10.1073/pnas.1511912112}.

\hyperdef{}{ref-DesjardinsProulx2013}{\label{ref-DesjardinsProulx2013}}
2. \textbf{Desjardins-Proulx P}, \textbf{White EP}, \textbf{Adamson JJ},
\textbf{Ram K}, \textbf{Poisot T}, \textbf{Gravel D}. 2013. The case for
open preprints in biology. PLoS Biology \textbf{11}:e1001563.
doi:\url{http://doi.org/10.1371/journal.pbio.1001563}.
